The \dealii Library, Version 9.1

### 2019-05-18 9.1/paper.tex
Add text about CUDA support

The GPU support was significantly extended for the current release. On the one hand, the MPI-parallel vector class
\texttt{LinearAlgebra::distributed::Vector} has gained a second template
argument \texttt{MemorySpace} which can either be \texttt{Host} or
\texttt{CUDA}. In the latter case, the data resides in the GPU memory. Also,
the ghost exchange can be performed completely via CUDA in case a compatible
MPI library is found (as is usual on large GPU-based supercomputers).

>>>>

The GPU support was significantly extended for the current release:
\begin{itemize}
  \item \texttt{LinearAlgebra::distributed::Vector}: the MPI-parallel vector
    class has gained a second template argument \texttt{MemorySpace} which can
    either be \texttt{Host} or \texttt{CUDA}. In the latter case, the data
    resides in the GPU memory. By default, the template parameter is
    \texttt{Host} and the behavior is unchanged compared to previous versions. 
    When using CUDA, the ghost exchange can be performed either by first copy
    the relevant data to the host, performing a MPI communication, and finally
    move the data to the device or, if CUDA-aware MPI is available, by
    performing the MPI directly from GPU to GPU.
  \item Constrained degrees of freedom: the matrix-free framework now now
    supports constraints degrees of freedom. The implementation is based on
    \cite{ljungkvist2017}. With this addition, not only the user can impose Dirichlet
    boundary conditions but the matrix-free framework can be used on adapted
    meshes. The only restriction is that for two-dimensional meshes, the degree
    of finite elements must be odd.  There is no such restriction in three
    dimensions.
  \item MPI matrix-free: using \texttt{LinearAlgebra::distributed::Vector}, the
    matrix-free framework can scale to multiple multiple GPUS by taking
    advantage of MPI. Each MPI process can only use GPU and therefore, if
    multiple GPUs are available in one node, it is necessary to have as many
    ranks as GPUs. Using Nvidia Multi-Process Device (MPS), it is also possible
    for multiple processes to use the same GPU. This can be advantageous if the
    amount of work on one rank is not sufficient to fully utilize GPU.
\end{itemize}
